---
title: "Metadata"
author: Tobie Surette
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{meta}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, include=FALSE}
library(gulf.utils)
```

# Setting Metadata Attributes

Metadata is defined as the data providing information about one or more aspects of the data; it is used to summarize basic information about data which can make tracking and working with specific data easier. Some examples include:

* Description of the study which generated the data
* Date and time data was observed
* Geographic region data was observed
* Purpose of the data
* Creator, author or custodian of the data
* Data variables, format and description.
* File format and size

Shown below is a simple example showing how to assign and retrieve metadata to an **R** dataset:

```{r}
# Define sample data set:
x <- data.frame(year = 2010:2014, site = letters[1:5], weight = exp(rnorm(5)), number = rpois(5,5))
```

There are then a number of methods via which we can assign various types of metadata:

```{r}# Define metadata attributes:
units(x, "weight") <- "kilogram"
desrciption(x) <- c(year = "Year of sampling", site = "Sampling site", weight = "Weight of specimen", number = "Number observed")
fmt(x, "year") <- "YYYY"
```

We can also assign an index key to our data. This attribut defines which variable(s) form a unique identifier for each row of the data frame.

```{r}
key(x) <- "year"
```

We can retrieve the set of metadata:
```{r}
metadata(x)
```

We can see how these metadata are stored as attributes:

```{r}
attributes(x)
```


